Fast and adaptive cointegration based model for forecasting financial time series

### 2017-12-10 slides/defense-slides.tex
Adding online component

>>>>

\begin{frame}
VECM can be solved using OLS. Using a sliding windows of data, the problem can be expressed as follows:

\[
\mathbf{X}(t) = 
\begin{bmatrix} 
\mathbf{x}_{t-L}^\intercal \\ \vdots \\ \mathbf{x}_t^\intercal
\end{bmatrix} \; , 
{\bf y}(t) = \begin{bmatrix} y_{t-L} \\ \vdots \\ y_t \end{bmatrix} \; .
\]

The optimal solution using a sliding windows is then:

\begin{equation}
{\bf w}(t)_*=({\bf X}(t)^\intercal{\bf X}(t))^{-1}{\bf X}(t)^\intercal{\bf y}(t) \, .
=\displaystyle \sum_{t=1}^L \mathbf{x}_t
\mathbf{x}_t^\intercal \displaystyle \sum_{t=1}^Ly_t \mathbf{x}_t
\end{equation}
\end{frame}

\begin{frame}
\begin{algorithm}[H]
\begin{algorithmic}[1]
\REQUIRE $\,$ \\
$\{\mathbf{x}_1,\dots,\mathbf{x}_m \}$: $m$ input vectors \\
$\{y_1,\dots,y_m \}$: $m$ targets \\
$L$: sliding window size ($L<m$) \\
\ENSURE  $\,$ \\
$\{f(\mathbf{x}_{L+1}),\dots,f(\mathbf{x}_m) \}$: model predictions \\
\STATE Initialize $\mathbf{A}=\displaystyle \sum_{t=1}^L \mathbf{x}_t
\mathbf{x}_t^\intercal + \gamma \mathbb{I}$
and $\mathbf{b}=\displaystyle \sum_{t=1}^Ly_t \mathbf{x}_t$
\FOR { $t = L+1$ to $m$ }
        \STATE read new $\mathbf{x}_t$
        \STATE $\mathbf{A} = \mathbf{A} + \mathbf{x}_t \mathbf{x}_t^\intercal-
\mathbf{x}_{t-L-1} \mathbf{x}_{t-L-1}^\intercal  $
        \STATE output prediction $f(\mathbf{x}_t) =  \mathbf{b}^\intercal
\mathbf{A}^{-1}\mathbf{x}_t$
        \STATE Read new $y_t$
        \STATE $\mathbf{b} = \mathbf{b} + y_t \mathbf{x}_t$
\ENDFOR

\end{algorithmic}
\caption{Recursive Ridge Regression}
\label{alg:SLAAR}
\end{algorithm}
\end{frame}
